For Induction-Induction, Induction is Enough

### 2019-11-10 paper/paper.tex
abstrac
Rks Ambrus
Streicher, Hugunin reference, edits etc

\documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling cleveref support, use "autoref"
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{todonotes}

@@

\title{For induction-induction, induction is enough} %TODO Please add

\titlerunning{For induction-induction, induction is enough}%optional, please use if title is longer than one line

@@

%TODO mandatory: add short abstract of the document
\begin{abstract}
  Inductive-inductive types (IITs) are a generalisation of inductive
  types in type theory. They allow the mutual definition of types with
  multiple sorts depending on each other. An example is the James
  Chapman-style syntax of type theory with conversion relations for
  each sort where e.g.\ the sort of types is indexed by contexts.  In
  previous work it was shown that all IITs can be constructed from a
  quotient inductive-inductive type (QIIT), namely the theory of IIT
  signatures. This theory is a small domain-specific type theory where
  a context is a signature for an IIT. In this paper we construct this
  theory of signatures only using inductive types. All of the
  constructions of this paper were formalised in the proof assistant
  Agda.
\end{abstract}

@@

Note by Ambrus: to be beautified, I only wanted to add the line of
thought.

@@

\subsection{Related work}

@@

\subsection{Structure of the paper}

We first define a \emph{theory of IIT signatures} in which every
context is a valid IIT signature (Section
\ref{sec:theory_of_signatures}). We present this type theory using an
algebraic \cite{ttintt} syntax, that is, as a quotient
inductive-inductive type (QIIT). In Section \ref{sec:ambroise} we show
that this QIIT can be constructed only using inductive types.

@@

UIP, funext, rewrite rules, version of Agda.

\section{The theory of IIT signatures}
\label{sec:theory_of_signatures}

@@

TODO: add examples where all the different constructors are used,
especially infinitary ones.

\section{Constructing the theory of IIT signatures}
\label{sec:ambroise}

@@

\paragraph{Construction}
\input{universaliit}

\section{Constructing all IITs from the theory IIT of signatures}
\label{sec:andras}

@@

\section{Further work}

@@

%%
%% Bibliography
%%

%% Please use bibtex,

@@

\appendix

\section{Styles of lists, enumerations, and descriptions}\label{sec:itemStyles}

List of different predefined enumeration styles:

\begin{itemize}
\item \verb|\begin{itemize}...\end{itemize}|
\item \dots
\item \dots
%\item \dots
\end{itemize}

\begin{enumerate}
\item \verb|\begin{enumerate}...\end{enumerate}|
\item \dots
\item \dots
%\item \dots
\end{enumerate}

\begin{alphaenumerate}
\item \verb|\begin{alphaenumerate}...\end{alphaenumerate}|
\item \dots
\item \dots
%\item \dots
\end{alphaenumerate}

\begin{romanenumerate}
\item \verb|\begin{romanenumerate}...\end{romanenumerate}|
\item \dots
\item \dots
%\item \dots
\end{romanenumerate}

\begin{bracketenumerate}
\item \verb|\begin{bracketenumerate}...\end{bracketenumerate}|
\item \dots
\item \dots
%\item \dots
\end{bracketenumerate}

\begin{description}
\item[Description 1] \verb|\begin{description} \item[Description 1]  ...\end{description}|
\item[Description 2] Fusce eu leo nisi. Cras eget orci neque, eleifend dapibus felis. Duis et leo dui. Nam vulputate, velit et laoreet porttitor, quam arcu facilisis dui, sed malesuada risus massa sit amet neque.
\item[Description 3]  \dots
%\item \dots
\end{description}

>>>>

\documentclass[a4paper,UKenglish,cleveref, autoref]{lipics-v2019}
%This is a template for producing LIPIcs articles.
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling cleveref support, use "autoref"
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{todonotes}
\presetkeys{todonotes}{inline}{}

@@

\title{For Induction-Induction, Induction is Enough} %TODO Please add

%% \titlerunning{For Induction-Induction, Induction is Enough}%optional, please use if title is longer than one line

@@

%TODO mandatory: add short abstract of the document
\begin{abstract}
  Inductive-inductive types (IITs) are a generalisation of inductive types in
  type theory. They allow the mutual definition of types with multiple sorts
  where later sorts can be indexed by previous ones. An example is the James
  Chapman-style syntax of type theory with conversion relations for each sort
  where e.g.\ the sort of types is indexed by contexts.  In previous work it was
  shown that all finitary IITs can be constructed from a quotient
  inductive-inductive type (QIIT), namely the theory of IIT signatures. This is
  a small domain-specific type theory where a context is a signature for an
  IIT. In this paper we construct this theory of signatures only using inductive
  types. We rely on function extensionality and uniqueness of identity
  proofs. All of the constructions of this paper were formalised in the proof
  assistant Agda.
\end{abstract}

@@

\todo{Note by Ambrus: to be beautified, I only wanted to add the line of
  thought.}

\todo{
  András: construction of infinitary IITs doesn't (yet) work. Should we drop
  infinitary functions from signatures?
  }

@@

\subsection{Related Work}

@@

\subsection{Structure of the Paper}

We first define a \emph{theory of IIT signatures} in which every context is a
valid IIT signature (Section \ref{sec:theory_of_signatures}). We present this
type theory as an algebraic \cite{ttintt} theory, specifically as a quotient
inductive-inductive type (QIIT). In Section \ref{sec:ambroise} we show that this
QIIT can be constructed only using inductive types.

@@

\todo{UIP, funext, rewrite rules, version of Agda.}

\section{The Theory of IIT Signatures}
\label{sec:theory_of_signatures}

@@

\todo[inline]{add examples where all the different constructors are used}

\section{Constructing the Theory of IIT Signatures}
\label{sec:ambroise}

\todo{Write this section}

@@

\paragraph*{Construction}
\input{universaliit}

\section{Constructing IITs from the Theory IIT of Signatures}
\label{sec:andras}

@@

\section{Further Work}

@@

@@
